Is statistical significance a thing?

### 2018-02-26 doc.tex
Update doc.tex

\mk{Unedited placeholder text}

@@

\begin{framed}
\begin{tabular}{p{7.5cm}p{7.5cm}}
     Language in published journal articles & Rewritten using the language of ``clarity'' \\
     	\hline
        \\
     \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
     	No relationship between individual genetic diversity and prevalence of avian malaria... & 
        The relationship between individual genetic diversity and prevalence of avian malaria was not
        statistically clear \\
        \\
     \multicolumn{2}{c}{\textbf{Using larger p~values as more evidence for something}} \\
        ...yielded nonsignificant differences on measures of those skills with P values of 
        at least 0.2, and most in the $0.7 \leq P \leq 0.9$ range. & 
        ...the differences between skills developed in treatment and control individuals
        were bot statistically clear ($p > 0.05$) \\
        \\
     \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ 
        but not in females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why
        there is a relationship between these variables in males, but not in females & 
        Substrate choice was positively correlated with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$,
        but this relationship was not statistically clear in females $(r_{s} = 0.32, N = 24, NS)$. A biological
        description comparing the correlation in males vs females is inappropriate without a direct test (in
        this case with the exact same correlation estimate, this is not a sensible test). \\
\end{tabular}
\end{framed}
   \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}

@@

\begin{itemize}
  \item Examples
  \subitem Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Singhetal.2017}
  \subitem Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}
  \subitem Complete lack of effect sizes: \citep{Juriadoetal.2017}
  \subitem Setting out to accept the null: \citep{Karulinetal.2015}
  \subitem ``...establish the \emph{a priori} selection of an effect level that is considered unacceptably toxic:'' \citep{Dentonetal.2011}
  \subitem With the \emph{correlation coefficient} for males and females (but significance for only one sex---``substrate 
  choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
  correlation would be significant for males but not females. \citep{MerilaitaandJormalainen1997}
\end{itemize}

>>>>

@@

\begin{framed}
\begin{tabular}{p{7.5cm}p{7.5cm}}
     Language in published journal articles & Rewritten using the language of ``clarity'' \\
     	\hline
        \\
     \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
        Cadmium bioaccumulates after acute exposure but has no effect on locomotion or shelter-seeking behaviour in the
        invasive green shore crab & Cadmium bioaccumulates after acute exposure but its effect on locomotion or shelter-seeking 
        behaviour in the invasive green shore crab was statistically unclear \\ 
        \\
        No effect of elevated carbon dioxide on reproductive behaviors in the three-spined stickleback & The effect of elevated 
        carbon dioxide on reproductive behaviors in the three-spined stickleback was statistically unclear \\
        \\
        The finding that bee species richness showed no significant relationship with the area of semi-natural habitat is 
        surprising because bee species richness is usually more strongly influenced by landscape context than pollination. & 
        Bee species richness is often found to be more strongly influenced by landscape context than pollination; however, 
        in the present study the relationship between bee species richness and area of semi-natural habitat was statistically 
        unclear \\ 
        \\
     \multicolumn{2}{c}{\textbf{P~values $\mathbf{> 0.05}$ should not be compared as evidence for anything}} \\
        ...yielded nonsignificant differences on measures of those skills with P values of at least 0.2, and most in the
        $0.7 \leq P \leq 0.9$ range. & ...the differences between skills developed in treatment and control individuals
        were not statistically clear ($p > 0.05$) \\
        \\
     \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ but not in
        females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why there is a relationship 
        between these variables in males, but not in females & Substrate choice was positively correlated with food choice in 
        males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this relationship was not statistically clear in females $(r_{s} = 0.32,
        N = 24, NS)$. A biological description comparing the correlation in males vs females is inappropriate without a direct
        test (in this case with the exact same correlation estimate, this is not a sensible test). \\
\end{tabular}
\end{framed}
   \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}

@@

\begin{itemize}
  \item Examples
  \subitem Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Bukovinszkyetal.2017, Singhetal.2017, Sundinetal.2017}
  \subitem Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}
  \subitem Complete lack of effect sizes: \citep{Juriadoetal.2017}
  \subitem Setting out to accept the null: \citep{Karulinetal.2015}
  \subitem ``...establish the \emph{a priori} selection of an effect level that is considered unacceptably toxic:'' \citep{Dentonetal.2011}
  \subitem With the \emph{correlation coefficient} for males and females (but significance for only one sex---``substrate 
  choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
  correlation would be significant for males but not females. \citep{MerilaitaandJormalainen1997}
\end{itemize}
